The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-04 paper/ms.tex
vsa changes

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Amalie Stokholm,$^{5}$
Allyson Bieryla,$^{8}$
David W. Latham,$^{8}$
Conny Aerts,$^{9,10,11}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Timothy R. Bedding,$^{12,5}$
Dominic M. Bowman,$^{10}$\newauthor
Ashley Chontos,$^{13}$
Gilbert A. Esquerdo,$^{8}$
Daniel Huber,$^{13}$
Paula Jofr\'{e},$^{14}$\newauthor
Madeline Lucey,$^{6}$
Simon J. Murphy,$^{12,5}$
Timothy van Reeth,$^{12,5}$\newauthor
Victor Silva Aguirre,$^{5}$
Jie Yu$^{12,5}$ 
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{11}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{12}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{14}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

In generating light curves of the \kepler smear stars, we have followed the methods described by \citet{smear}, with some improvements. We selected our input RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and queried MAST to find the corresponding mean pixel position for each \kepler quarter. We then measured the centroid of smear columns in the vicinity, and used these values to do raw aperture photometry. We found that the cosine-bell aperture used for raw photometry by \citet{smear} can sometimes introduce position-dependent systematics and jumps. We instead used a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ is the width in pixels. The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts. The super-Gaussian is calculated on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid. We then extracted photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.

From this raw photometry a background light curve was subtracted, correcting for time-varying global systematics. Whereas in \citet{smear} we subtracted a background estimated manually, for this larger set of light curves, we have chosen the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and taken our background level to be the median of this at each time sample. To reduce the noise in this background model, we fitted a Gaussian Process with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.

@@

\begin{equation}
\label{scaling}
\numax \propto \dfrac{g}{g_{\sun}} \cdot \left(\dfrac{\teff}{\teff_{\sun}}\right)^{\dfrac{1}{2}}
\end{equation}

@@

\begin{equation}
\label{Dnuscaling}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}
\end{equation}

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. B.P. also acknowledges support from Balliol College and the Clarendon Fund. D.H. acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000). DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory. The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE). Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106).

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Amalie Stokholm,$^{5}$
Allyson Bieryla,$^{8}$
David W. Latham,$^{8}$
Conny Aerts,$^{9,10,11}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Timothy R. Bedding,$^{12,5}$
Dominic M. Bowman,$^{9}$\newauthor
Ashley Chontos,$^{13}$
Gilbert A. Esquerdo,$^{8}$
Daniel Huber,$^{13}$
Paula Jofr\'{e},$^{14}$\newauthor
Madeline Lucey,$^{6}$
Simon J. Murphy,$^{12,5}$
Timothy van Reeth,$^{12,5}$\newauthor
Victor Silva Aguirre,$^{5}$
Jie Yu$^{12,5}$ 
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{11}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{12}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{14}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

In generating light curves of the \kepler smear stars, we have followed the methods described by \citet{smear}, with some improvements. We selected our input RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and queried MAST to find the corresponding mean pixel position for each \kepler quarter. We then measured the centroid of smear columns in the vicinity, and used these values to do raw aperture photometry. We found that the cosine-bell aperture used for raw photometry by \citet{smear} can sometimes introduce position-dependent systematics and jumps. We instead used a super-Gaussian aperture,

\begin{equation}
A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4},
\end{equation}
\noindent where $x_0$ is the centroid and $w$ is the width in pixels. The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts. The super-Gaussian is calculated on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid. We then extracted photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.

From this raw photometry a background light curve was subtracted, correcting for time-varying global systematics. Whereas in \citet{smear} we subtracted a background estimated manually, for this larger set of light curves, we have chosen the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and taken our background level to be the median of this at each time sample. To reduce the noise in this background model, we fitted a Gaussian Process (GP) with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.

@@

\begin{equation}
\label{scaling}
\numax \propto \dfrac{g}{g_{\sun}} \cdot \left(\dfrac{\teff}{\teff_{\sun}}\right)^{\dfrac{1}{2}},
\end{equation}

@@

\begin{equation}
\label{Dnuscaling}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}.
\end{equation}

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. B.P. also acknowledges support from Balliol College and the Clarendon Fund. D.H. acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000). DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory. The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE). V.S.A. acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B). Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106).
